Bandit Multiclass Linear Classification: \\ Efficient Algorithms for the Separable Case

### 2019-02-05 arxiv/appendix-experiment.tex
widened the eqns

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{\textsc{Banditron}'s final decision boundaries}
     \label{fig:banditron-points}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}'s final decision boundaries}
    \label{fig:linearova-points}
\end{figure}
%Our Algorithm with linear kernel (
%To better understand how each algorithm works,
%Our Algorithm with rational kernel (

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \vspace*{-0.2cm}
    \caption{Algorithm~\ref{algorithm:kernelized} (with rational kernel)'s final decision boundaries}
    \label{fig:rationalova-points}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_banditron_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_banditron_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{\textsc{Banditron}'s final decision boundaries}
     \label{fig:banditron-points}
\end{figure}

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_linear_ova_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_linear_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}'s final decision boundaries}
    \label{fig:linearova-points}
\end{figure}
%Our Algorithm with linear kernel (
%To better understand how each algorithm works,
%Our Algorithm with rational kernel (

\begin{figure}[h!]
    \centering
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \begin{center}
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_rational_ova_points}
        \caption{Strongly separable case}
        \end{center}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \captionsetup{justification=centering}
        \centering
        \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_rational_ova_points}
         \caption{Weakly separable case}
    \end{subfigure}
    \captionsetup{justification=centering}
    \caption{Algorithm~\ref{algorithm:kernelized} (with rational kernel)'s final decision boundaries}
    \label{fig:rationalova-points}
\end{figure}

### 2019-02-05 arxiv/empirical-comparison.tex
widened the eqns

\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.23\textwidth}
\captionsetup{justification=centering}
\begin{center}
\hspace*{-0.3cm} \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
\caption{Strongly separable case}
\label{figure:strongly-separable-dataset}
\end{center}
\end{subfigure}
\hfill
\begin{subfigure}[b]{0.23\textwidth}
\captionsetup{justification=centering}
\centering
\hspace*{-0.3cm}  \includegraphics[width=1.15\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
\caption{Weakly separable case}
\label{figure:weakly-separable-dataset}
\end{subfigure}
\vspace*{-0.2cm}
\caption{Strongly and weakly linearly separable datasets in $\R^3$ with $K=3$
classes and $T=5\times 10^6$ examples. Here we show projections of the examples
onto their first two coordinates, which lie in the ball of radius $1/\sqrt{2}$
centered at the origin. The third coordinate is $1/\sqrt{2}$ for all examples.
Class 1 is depicted red. Classes 2 and 3 are depicted green and blue,
respectively. $80\%$ of the examples belong to class 1, $10\%$ belong to class 2
and $10\%$ belong to class 3. Class 1 lies in the angle interval $[-15^\circ,
15^\circ]$, while classes 2 and 3 lie in the angle intervals $[15^\circ,
180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. The examples are
strongly and weakly linearly separable with a margin of $\gamma=0.05$,
respectively. (Examples lying within margin $\gamma$ of the linear separators
were rejected during sampling.)}
\label{figure:strongly-and-weakly-separable-datasets}
\end{figure}

>>>>

\begin{figure}[h]
  \centering
\begin{subfigure}[b]{0.3\textwidth}
\captionsetup{justification=centering}
\begin{center}
\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/strong_points}
\caption{Strongly separable case}
\label{figure:strongly-separable-dataset}
\end{center}
\end{subfigure}
\begin{subfigure}[b]{0.3\textwidth}
\captionsetup{justification=centering}
\centering
\includegraphics[width=\textwidth, trim={0, 0cm, 0, 0}, clip]{figures/weak_points}
\caption{Weakly separable case}
\label{figure:weakly-separable-dataset}
\end{subfigure}
\caption{Strongly and weakly linearly separable datasets in $\R^3$ with $K=3$
classes and $T=5\times 10^6$ examples. Here we show projections of the examples
onto their first two coordinates, which lie in the ball of radius $1/\sqrt{2}$
centered at the origin. The third coordinate is $1/\sqrt{2}$ for all examples.
Class 1 is depicted red. Classes 2 and 3 are depicted green and blue,
respectively. $80\%$ of the examples belong to class 1, $10\%$ belong to class 2
and $10\%$ belong to class 3. Class 1 lies in the angle interval $[-15^\circ,
15^\circ]$, while classes 2 and 3 lie in the angle intervals $[15^\circ,
180^\circ]$ and $[-180^\circ, -15^\circ]$ respectively. The examples are
strongly and weakly linearly separable with a margin of $\gamma=0.05$,
respectively. (Examples lying within margin $\gamma$ of the linear separators
were rejected during sampling.)}
\label{figure:strongly-and-weakly-separable-datasets}
\end{figure}

### 2019-02-05 arxiv/mistake-lower-bound-for-ignorant-algorithms.tex
widened the eqns

To formally define ignorant algorithms, we define the conditional distribution
from which an algorithm draws its predictions. Formally, given an algorithm
$\calA$ and an adversarial strategy, we define
\begin{multline*}
p_t(y|x) = \\
\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] \; .
\end{multline*}
In other words, in any round $t$, conditioned on the past $t-1$ rounds, the
algorithm $\calA$ chooses $y_t$ from probability distribution $p_t(\cdot|x_t)$.
Formally, $p_t$ is a function $p:\{1,2,\dots,K\} \times \R^d \to [0,1]$
such that $\sum_{y=1}^K p_t(y|x) = 1$ for any $x \in \R^d$.

\begin{definition}[Ignorant algorithm]
An algorithm $\calA$ for \textsc{Online Multiclass Linear Classification with
Bandit Feedback} is called \emph{ignorant} if for every $t=1,2,\dots,T$,
$p_t$ is determined solely by the sequence
$(x_{a_1}, y_{a_1}), (x_{a_2}, y_{a_2}), \dots, (x_{a_n}, y_{a_n})$
of labeled examples
from the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
the algorithm makes a correct prediction.
\end{definition}

@@

To explain the definition, consider an ignorant algorithm $\calA$. Suppose that
on a sequence of examples $(x_1, y_1), (x_2, y_2), \dots, (x_{t-1}, y_{t-1})$
generated by some adversary the algorthm $\calA$ makes correct predictions in
rounds $a_1, a_2, \dots, a_n$ where $1 \le a_1 < a_2 < \dots < a_n < t$ and
errors on rounds $\{1,2,\dots,t-1\} \setminus \{a_1, a_2, \dots, a_n\}$. Suppose
that on another sequence of examples $(x_1', y_1'), (x_2', y_2'), \dots,
(x_{s-1}', y_{s-1}')$ generated by another adversary the algorithm $\calA$ makes
correct predictions in rounds $b_1, b_2, \dots, b_n$ where $1 \le b_1 < b_2 <
\dots < b_n < s$ and errors on rounds $\{1,2,\dots,s-1\} \setminus \{b_1, b_2,
\dots, b_n\}$. Futhermore, suppose
\begin{align*}
(x_{a_1}, y_{a_1}) &= (x'_{b_1}, y'_{b_1}) \; , \\
(x_{a_2}, y_{a_2}) &= (x'_{b_2}, y'_{b_2}) \; , \\
\vdots \\
(x_{a_n}, y_{a_n}) &= (x'_{b_2}, y'_{b_n}) \; .
\end{align*}
Then, the definition
\begin{multline*}
\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] = \\
\Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x] \; .
\end{multline*}
Note that the sequences $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1},
y_{t-1})$ and $(x_1', y_1')$, $(x_2', y_2')$, $\dots$, $(x_{s-1}', y_{s-1}')$
might have different lengths and and $\calA$ might error in different sets of
rounds. As a special case, if an ignorant algorithm makes a mistake in round $t$
then $p_{t+1}=p_t$.

@@

\begin{lemma}
\label{lemma:embed_d_gamma}
Let $\gamma \in (0,\frac{1}{160})$, let $d$ be a positive integer and let $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$.
There exist vectors $u_1, u_2, \dots, u_N, v_1, v_2, \dots, v_N \in \R^d$ such that for all $i, j \in \{1,2,\dots,N\}$,
\begin{align*}
\norm{u_i} & \le 1 \; , \\
\norm{v_j} & \le 1 \; , \\
\ip{u_i}{v_j} & \ge \gamma & & \text{if $i=j$,} \\
\ip{u_i}{v_j} & \le -\gamma & & \text{if $i \neq j$.}
\end{align*}
\end{lemma}

\begin{proof}
By Lemma 6 of~\citet{Long-1995}, there exists vectors $z_1, z_2, \dots, z_N \in
\R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots = \norm{z_N} = 1$ and the
angle between the vectors is $\measuredangle(z_i, z_j) \ge \sqrt{40 \gamma}$ for
$i \neq j$, $i,j \in \{1,2,\dots,N\}$. Since $\cos\theta \le 1-\theta^2/5$ for
any $\theta \in [-\pi,\pi]$, this implies that
\begin{align*}
\ip{z_i}{z_j} &= 1 && \text{if $i = j$,} \\
\ip{z_i}{z_j} &\le 1 - 8\gamma && \text{if $i \neq j$.}
\end{align*}

Define $v_i = (\frac{1}{2} z_i, \frac{1}{2})$, and $u_i = (\frac{1}{2} z_i,
-\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$. It can be easily
checked that for all $i$, $\norm{v_i} \le 1$ and $\norm{u_i} \le 1$.
Additionally,
$$
\ip{u_i}{v_j} = \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \; .
$$
Thus,
\begin{align*}
\ip{u_i}{v_j} &\ge \gamma && \text{if $i=j$,} \\
\ip{u_i}{v_j} &\le -\gamma && \text{if $i \neq j$.}
\end{align*}
\end{proof}

@@

Let $\tau$ be the time step $t$ in which the adversary sets $\textsc{phase}\leftarrow 2$.
If the adversary never sets $\textsc{phase}\leftarrow 2$, we define $\tau = T + 1$.
Then,
\begin{align}
& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge \Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right]
+ \Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \; .
\end{align}
We upper bound each of last two terms separately.

@@

Combining the two, we have that
\begin{align*}
& \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] \nonumber \\
& \ge q_0 \Exp[\tau - 1] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\
& =  \Exp \left[ \Exp \left[ q_0 (\tau - 1) + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
\end{align*}
We lower bound the last expression by considering two cases for $\tau$.
If $\tau \ge \frac{1}{2}T + 1$, then the last expression is lower bounded by
$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. If
$\tau < \frac{1}{2}T+1$, it is lower bounded by
\begin{align*}
& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}T}\right) \\
& = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
& \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
& \ge \frac{1}{10} \sqrt{T} \; .
\end{align*}

>>>>

To formally define ignorant algorithms, we define the conditional distribution
from which an algorithm draws its predictions. Formally, given an algorithm
$\calA$ and an adversarial strategy, we define
\[
p_t(y|x) = \\
\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] \; .
\]
In other words, in any round $t$, conditioned on the past $t-1$ rounds, the
algorithm $\calA$ chooses $y_t$ from probability distribution $p_t(\cdot|x_t)$.
Formally, $p_t$ is a function $p:\{1,2,\dots,K\} \times \R^d \to [0,1]$
such that $\sum_{y=1}^K p_t(y|x) = 1$ for any $x \in \R^d$.

\begin{definition}[Ignorant algorithm]
An algorithm $\calA$ for \textsc{Online Multiclass Linear Classification with
Bandit Feedback} is called \emph{ignorant} if for every $t=1,2,\dots,T$,
$p_t$ is determined solely by the sequence
$(x_{a_1}, y_{a_1})$,$(x_{a_2}, y_{a_2})$, $\dots$, $(x_{a_n}, y_{a_n})$
of labeled examples
from the rounds $1 \le a_1 < a_2 < \dots < a_n < t$ in which
the algorithm makes a correct prediction.
\end{definition}

@@

To explain the definition, consider an ignorant algorithm $\calA$. Suppose that
on a sequence of examples $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1}, y_{t-1})$
generated by some adversary the algorthm $\calA$ makes correct predictions in
rounds $a_1, a_2, \dots, a_n$ where $1 \le a_1 < a_2 < \dots < a_n < t$ and
errors on rounds $\{1,2,\dots,t-1\} \setminus \{a_1, a_2, \dots, a_n\}$. Suppose
that on another sequence of examples $(x_1', y_1'), (x_2', y_2'), \dots,
(x_{s-1}', y_{s-1}')$ generated by another adversary the algorithm $\calA$ makes
correct predictions in rounds $b_1, b_2, \dots, b_n$ where $1 \le b_1 < b_2 <
\dots < b_n < s$ and errors on rounds $\{1,2,\dots,s-1\} \setminus \{b_1, b_2,
\dots, b_n\}$. Futhermore, suppose
\begin{align*}
(x_{a_1}, y_{a_1}) &= (x'_{b_1}, y'_{b_1}) \; , \\
(x_{a_2}, y_{a_2}) &= (x'_{b_2}, y'_{b_2}) \; , \\
\vdots \\
(x_{a_n}, y_{a_n}) &= (x'_{b_2}, y'_{b_n}) \; .
\end{align*}
Then, as $\calA$ is ignorant,
\[
\Pr[y_t = y ~|~ (x_1, y_1), (x_2, y_2) \dots, (x_{t-1}, y_{t-1}), x_t = x] =
\Pr[y_t' = y ~|~ (x_1', y_1'), (x_2', y_2') \dots, (x_{t-1}', y_{t-1}'), x_t' = x] \; .
\]
Note that the sequences $(x_1, y_1)$, $(x_2, y_2)$, $\dots$, $(x_{t-1},
y_{t-1})$ and $(x_1', y_1')$, $(x_2', y_2')$, $\dots$, $(x_{s-1}', y_{s-1}')$
might have different lengths and and $\calA$ might error in different sets of
rounds. As a special case, if an ignorant algorithm makes a mistake in round $t$
then $p_{t+1}=p_t$.

@@

\begin{lemma}
\label{lemma:embed_d_gamma}
Let $\gamma \in (0,\frac{1}{160})$, let $d$ be a positive integer and let $N = (\frac{1}{2\sqrt{40\gamma}})^{d-2}$.
There exist vectors $u_1, u_2, \dots, u_N$, $v_1, v_2, \dots, v_N$ in $\R^d$ such that for all $i, j \in \{1,2,\dots,N\}$,
\begin{align*}
\norm{u_i} & \le 1 \; , \\
\norm{v_j} & \le 1 \; , \\
\ip{u_i}{v_j} & \ge \gamma, \quad \text{if $i=j$,} \\
\ip{u_i}{v_j} & \le -\gamma, \quad \text{if $i \neq j$.}
\end{align*}
\end{lemma}

\begin{proof}
By Lemma 6 of~\citet{Long-1995}, there exists vectors $z_1, z_2, \dots, z_N \in
\R^{d-1}$ such that $\norm{z_1} = \norm{z_2} = \dots = \norm{z_N} = 1$ and the
angle between the vectors is $\measuredangle(z_i, z_j) \ge \sqrt{40 \gamma}$ for
$i \neq j$, $i,j \in \{1,2,\dots,N\}$. Since $\cos\theta \le 1-\theta^2/5$ for
any $\theta \in [-\pi,\pi]$, this implies that
\begin{align*}
\ip{z_i}{z_j} &= 1, \quad \text{if $i = j$,} \\
\ip{z_i}{z_j} &\le 1 - 8\gamma, \quad \text{if $i \neq j$.}
\end{align*}

Define $v_i = (\frac{1}{2} z_i, \frac{1}{2})$, and $u_i = (\frac{1}{2} z_i,
-\frac{1}{2}(1-4\gamma))$ for all $i \in \{1,2,\dots,N\}$. It can be easily
checked that for all $i$, $\norm{v_i} \le 1$ and $\norm{u_i} \le 1$.
Additionally,
$$
\ip{u_i}{v_j} = \frac{1}{4} \ip{z_i}{z_j} - \frac {1-4\gamma} 4 \; .
$$
Thus,
\begin{align*}
\ip{u_i}{v_j} &\ge \gamma, \quad \text{if $i=j$,} \\
\ip{u_i}{v_j} &\le -\gamma, \quad \text{if $i \neq j$.}
\end{align*}
\end{proof}

@@

Let $\tau$ be the time step $t$ in which the adversary sets $\textsc{phase}\leftarrow 2$.
If the adversary never sets $\textsc{phase}\leftarrow 2$, we define $\tau = T + 1$.
Then,
\begin{align*}
 \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right]
 \ge \Exp\left[\sum_{t=1}^{\tau - 1} \indicator{\widehat y_t\neq y_t}\right]
+ \Exp\left[\sum_{t=\tau}^T \indicator{\widehat y_t\neq y_t}\right] \; .
\end{align*}
We upper bound each of last two terms separately.

@@

Combining the two, we have that
\begin{align*}
 \Exp \left[\sum_{t=1}^T \indicator{\widehat y_t\neq y_t}\right] 
& \ge q_0 \Exp[\tau - 1] + \Exp \left[\frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right)\right] \\
& =  \Exp \left[ \Exp \left[ q_0 (\tau - 1) + \frac{1-q_0}{q_0}\left(1-(1-q_0)^{T-\tau+1}\right) ~\middle|~ \tau \right] \right] \; .
\end{align*}
We lower bound the last expression by considering two cases for $\tau$.
If $\tau \ge \frac{1}{2}T + 1$, then the last expression is lower bounded by
$\frac{1}{2}q_0 T = \frac{1}{2} \sqrt{T}$. If
$\tau < \frac{1}{2}T+1$, it is lower bounded by
\begin{align*}
& \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2}T}\right) \\
& = \frac{1-q_0}{q_0}\left(1-(1-q_0)^{\frac{1}{2q_0^2}}\right) \\
& \ge \frac{1-\frac{1}{\sqrt{2}}}{q_0}\left(1-\frac{1}{\sqrt{e}}\right) \\
& \ge \frac{1}{10} \sqrt{T} \; .
\end{align*}
